---
title: "Model Comparison"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Values

Import values computed from Model Building .

```{r importvar, eval=FALSE}
# read files
source(file.path("datasets", "model.R"))
```

```{r importvar2, include=FALSE}
# read files
source(file.path("datasets", "model.R"))
```

## Model Comparison

It is not apparent which is the better model, since the model weights are approximately the same.

We can conclude that **the effect of movie type** is as significant as a predictor as **the effect of box office results** and **the effect of movie scores** on **crime rates**.

```{r compare}
# compare models 
compare(m1, m2) 
```

## Model Averaging

Merge datasets d1 and d2 to create prediction data.

```{r merge}
# combine d1, d2
d = merge(d1,d2)

```

### Model 1

Find significant predictors of Model 1 with summary. As shown below, predictor **Bx3_c** is the most significant, and hence we will examine **the effect of movie type - "Neutral"** on **log crime cases**.

```{r m1.summary}
summary(lm(log_crime~ Bx1_c + Bx2_c + Bx3_c, data=d1, x=T))
```

Plot the model-averaged predictions of this model set.

```{r m1.average}
# Model 1
Bx3_c.seq <- seq(from=-5.5, to=4, length.out = 30)
d.predict <- list(
  log_crime = rep(0,30),
  Bx1_c = rep(0,30),
  Bx2_c = rep(0,30),
  Bx3_c = Bx3_c.seq,
  log_box_office = rep(0,30),
  score.s = rep(0,30),
  Bscore.s = rep(0,30)
)

  pred.m <- link( m1 , data=d.predict )
  mu <- apply( pred.m , 2 , mean )
  mu.PI <- apply( pred.m , 2 , PI )
  
  plot( log_crime ~ Bx3_c , d , col=rangi2 )
  lines( Bx3_c.seq , mu , lty=2 )
  lines( Bx3_c.seq, mu.PI[1,] , lty=2 )
  lines( Bx3_c.seq , mu.PI[2,] , lty=2 )
  
  log_crime.ensemble <- ensemble( m1 , m2 ,data=d.predict )
  mu <- apply( log_crime.ensemble$link , 2 , mean )
  mu.PI <- apply( log_crime.ensemble$link , 2 , PI )
  lines( Bx3_c.seq , mu )
  shade( mu.PI , Bx3_c.seq )
  
```

### Model 2

Find significant predictors of Model 2 with summary. As shown below, predictor **log_box_office** is the most significant, and hence we will examine **the effect of log box office results** on **log crime cases**.

```{r m2.summary}
summary(lm(log_crime~ log_box_office + score.s + Bscore.s, data=d2, x=T))
```

Plot the model-averaged predictions of this model set.

```{r m2.average}
# Model 2
log_box_office.seq <- seq(from=16, to=18, length.out = 30)
d.predict <- list(
  log_crime = rep(0,30),
  Bx1_c = rep(0,30),
  Bx2_c = rep(0,30),
  Bx3_c = rep(0,30),
  log_box_office = log_box_office.seq,
  score.s = rep(0,30),
  Bscore.s = rep(0,30)
)

  pred.m <- link( m2 , data=d.predict )
  mu <- apply( pred.m , 2 , mean )
  mu.PI <- apply( pred.m , 2 , PI )
  
  plot( log_crime ~ log_box_office , d , col=rangi2 )
  lines( log_box_office.seq , mu , lty=2 )
  lines( log_box_office.seq, mu.PI[1,] , lty=2 )
  lines( log_box_office.seq , mu.PI[2,] , lty=2 )
  
  log_crime.ensemble <- ensemble( m1 , m2 ,data=d.predict )
  mu <- apply( log_crime.ensemble$link , 2 , mean )
  mu.PI <- apply( log_crime.ensemble$link , 2 , PI )
  lines( log_box_office.seq , mu )
  shade( mu.PI , log_box_office.seq )
```
