---
title: "Data Mining"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

Load all required packages.

```{r library, include=FALSE}
require("xml2")
library('rvest')
library('NLP')
library('tm')
library('stringr')
library('dplyr')
library("DT")
```

## Import Data

Import the datasets of *Taipei's Top 15 Movies From 2008-2015 (by quarter)* and combine.

```{r import}
# read files
Q1 = read.csv(file.path("datasets", "QBS-Q1-data-new.csv"))
Q2 = read.csv(file.path("datasets", "QBS-Q2-data-new.csv"))
Q3 = read.csv(file.path("datasets", "QBS-Q3-data-new.csv"))
Q4 = read.csv(file.path("datasets", "QBS-Q4-data-new.csv"))
Y = read.csv(file.path("datasets", "Crime-Rate.csv"))

# combine datasets
data = rbind(Q1,Q2,Q3,Q4)

DT:::datatable(
    data,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=4)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 4)
                  )
              )
```

.

## Preprocess Data

Step 1 : Convert variables **box_office**, **rotten_tomatoes**, and **Imbd** to their correct numeric values. 

Step 2 : Compute the log of **box_office** for better comparison.

Step 3 : Since many Rotten Tomatoes scores are missing, we decided to overwrite them with their corresponding Imbd scores. We then compute and assign the mean scores to variable **score**. 

Step 4 : Standardize scores for better comparison.

```{r pre}
# convert factor to numeric
data$box_office = as.numeric(data$box_office)
data$rotten_tomatoes = as.numeric(data$rotten_tomatoes)
data$Imbd = as.numeric(data$Imbd)

# convert box office to log for better comparison
data$log_box_office = log(data$box_office)

# compute mean score and overwrite NA values
A = (data$rotten_tomatoes + data$Imbd)/2
B = data$Imbd
data$score = ifelse(!is.na(data$rotten_tomatoes), A, B)

# extract data with complete log box office and score values
data = data[complete.cases(data[ , 8:9]), ]

# standardize score
data$score.s = (data$score - mean(data$score))/sd(data$score)

DT:::datatable(
    data,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=4)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 4)
                  )
              )
```

.

Since the variable **category** consists of jumbles of genres, we must apply text mining techniques to derive information.
The process of transforming and cleaning text data is shown below.

```{r tm}
category <- data$category
corpus <- Corpus(VectorSource(category))

## Data-Preprocessing: removing punctuation
corpus2 <- tm_map(corpus, removePunctuation)
## Data-Preprocessing: changing all to lower case
corpus2 <- tm_map(corpus2, tolower)
## Data-Preprocessing: removing whitespaces
corpus2 <- tm_map(corpus2, stripWhitespace)
corpus2 = sapply(corpus2, as.character)

data$category =as.factor(corpus2)

DT:::datatable(
    data,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=4)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 4)
                  )
              )
```

.

## Define Variables

According to their genres, movies are categorized into three types: crime-inducing, crime-reducing, and neutral.

Their corresponding genres are as follows:

1. Crime-inducing: "crime","thriller","horror","mystery","suspense". These are the genres that we assume will induce negative emotions, likely leading to an increase in crime rates.

2. Crime-reducing: "family","kids","comedy","animation". These are the genres that we assume will evoke positive emotions, which may cause a decrease in crime rates.

3. Neutral: these are the genres that fall in neither category.

```{r var}
# determine x1=number of crime-inducing movies
x1 = c("crime","thriller","horror","mystery","suspense")
x1 = paste(x1, collapse='|')
x1_row = which(apply(data.frame(data$category), 1, function(i) str_detect(paste(i, collapse=','), x1)))
for(i in 1:481){
  if (i %in% x1_row){
    data[i,"x1"] = 1
  } else{
   data[i,"x1"] = 0
  }
}

# determine x2=number of crime-reducing movies
x2 = c("family","kids","comedy","animation")
x2 = paste(x2, collapse='|')
x2_row = which(apply(data.frame(data$category), 1, function(i) str_detect(paste(i, collapse=','), x2)))
for(i in 1:481){
  if (i %in% x2_row){
    data[i,"x2"] = 1
  } else{
    data[i,"x2"] = 0
  }
}

# determine x3=number of neutral movies
data$x3 = ifelse(data$x1 +data$x2 == 0, 1, 0)

DT:::datatable(
    data,
    extensions = list("Scroller" = NULL,
                      'FixedHeader' = NULL,
                      "FixedColumns" = list(leftColumns=4)),
    options = list(
                deferRender = TRUE,
                scrollY = 200,
                scroller = TRUE,
                autoWidth=TRUE,
                pageLength = 50,
                fixedHeader = TRUE,
                dom = 't',
                scrollX = TRUE,
                fixedColumns = list(leftColumns = 4)
                  )
              )
```

.

## Assign to Datasets

For our first model, we will examine **the effect of movie type** on **crime rates**. **The effect of movie type** is the average log box office value for each type.

```{r model1, eval=FALSE}
# Model 1:
extract.data = data %>%
  group_by(year, Quarter) %>%
  summarise(Bx1=mean(log_box_office*x1), Bx2=mean(log_box_office*x2), Bx3=mean(log_box_office*x3)) %>%
  select(year, Quarter, Bx1, Bx2, Bx3)

extract.data = merge(Y, extract.data, by=c("year","Quarter"))

write.csv(extract.data, "M1.data.new.csv")
```

For our second model, we will examine **the effect of box office results** and **the effect of movie scores** on **crime rates**.

```{r model2, eval=FALSE}
# Model 2:
extract.data = data %>%
  group_by(year, Quarter) %>%
  summarise(log_box_office=mean(log_box_office), score.s = mean(score.s), Bscore.s=mean(log_box_office*score.s)) %>%
  select(year, Quarter, log_box_office, score.s, Bscore.s) 

extract.data = merge(Y, extract.data, by=c("year","Quarter"))

write.csv(extract.data, "M2.data.new.csv")
```
