---
title: "Model Building"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

Load all required packages.

```{r library}
library(readr)
library(rstan)
library(rethinking)
```

## Model 1

### Building Model 1

#### Import Data

Import the Model 1 Dataset.

```{r import.m1}
# read files
data1 = read.csv(file.path("datasets", "M1.data.new.csv"))
```

#### Preprocess Data

```{r pre.m1}
d1 = data.frame(cbind(data1$Total_cases_Number, data1$Bx1, data1$Bx2, data1$Bx3))
names(d1) = c("Total_cases_Number","Bx1","Bx2","Bx3") 

d1$crime_cases = (d1$Total_cases_Number - mean(d1$Total_cases_Number))/sd(d1$Total_cases_Number)
```

#### Build Model

Build Model 1 with map.

```{r m1}
# Method 1
m1 <- map(
  alist(
    crime_cases ~ dnorm(mu, sigma),
    mu <- a +b1*Bx1 + b2*Bx2 + b3*Bx3,
    a ~ dnorm(0,10),
    b1 ~ dnorm(0,10),
    b2 ~ dnorm(0,10),
    b3 ~ dnorm(0,10),
    sigma ~ dunif(0,10)
  ),
  data <- d1,
  start<-list(a=mean(d1$crime_cases),b1=0,b2=0,b3=0, sigma=sd(d1$crime_cases)))
```

### Examining Model 1

#### Parameter Overview

From the pairs plot below, we can see that 

```{r m1.pairs}
pairs(m1)
```

We then examine the parameter estimates of Model 1.

```{r m1.precis}
precis(m1)
```

#### Parameter Effects

The effect of movie types are shown below:

1. Crime-inducing: Bx1

```{r m1.bx1}
Bx1.seq <- seq(from = 0, to = 10, length.out = 100)
mu <- link(m1, data = data.frame(Bx1 = Bx1.seq, Bx2 = mean(d1$Bx2), Bx3 = mean(d1$Bx3)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx1, data = d1)
lines(Bx1.seq, mu.mean)

shade(mu.PI, Bx1.seq)
```

2. Crime-reducing: Bx2

```{r m1.bx2}
Bx2.seq <- seq(from = 0, to = 111, length.out = 100)
mu <- link(m1, data = data.frame(Bx2 = Bx2.seq, Bx1 = mean(d1$Bx1), Bx3 = mean(d1$Bx3)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx2, data = d1)
lines(Bx2.seq, mu.mean)

shade(mu.PI, Bx2.seq)
```

3. Neutral: Bx3

```{r m1.bx3}
Bx3.seq <- seq(from = 0, to = 11, length.out = 100)
mu <- link(m1, data = data.frame(Bx3 = Bx3.seq, Bx1 = mean(d1$Bx1), Bx2 = mean(d1$Bx2)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx3, data = d1)
lines(Bx3.seq, mu.mean)

shade(mu.PI, Bx3.seq)
```

## Model 1 With Stan

### Building Model 1 With Stan

#### Build Model

Build Model 1 with map2stan.

```{r m1.stan}
# Method 2
m1.stan <- map2stan( m1, data<-d1, iter = 1e4, warmup = 1000) 
```

### Examining Model 1 With Stan

#### Parameter Overview

From the pairs plot below, we can see that 

```{r m1.stan.pairs}
pairs(m1.stan)
```

We then examine the parameter estimates of Model 1 with Stan.

```{r m1.stan.precis}
precis(m1.stan)
```

#### Parameter Effects

The effect of movie types are shown below:

1. Crime-inducing: Bx1

```{r m1.stan.bx1}
Bx1.seq <- seq(from = 0, to = 10, length.out = 100)
mu <- link(m1.stan, data = data.frame(Bx1 = Bx1.seq, Bx2 = mean(d1$Bx2), Bx3 = mean(d1$Bx3)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx1, data = d1)
lines(Bx1.seq, mu.mean)

shade(mu.PI, Bx1.seq)
```

2. Crime-reducing: Bx2

```{r m1.stan.bx2}
Bx2.seq <- seq(from = 0, to = 111, length.out = 100)
mu <- link(m1.stan, data = data.frame(Bx2 = Bx2.seq, Bx1 = mean(d1$Bx1), Bx3 = mean(d1$Bx3)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx2, data = d1)
lines(Bx2.seq, mu.mean)

shade(mu.PI, Bx2.seq)
```

3. Neutral: Bx3

```{r m1.stan.bx3}
Bx3.seq <- seq(from = 0, to = 11, length.out = 100)
mu <- link(m1.stan, data = data.frame(Bx3 = Bx3.seq, Bx1 = mean(d1$Bx1), Bx2 = mean(d1$Bx2)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bx3, data = d1)
lines(Bx3.seq, mu.mean)

shade(mu.PI, Bx3.seq)
```

## Model 2

### Building Model 2

#### Import Data

Import the Model 2 Dataset.

```{r import.m2}
# read files
data2 = read.csv(file.path("datasets", "M2.data.new.csv"))
```

#### Preprocess Data

```{r pre.m2}
box_office = exp(data2$log_box_office)
std_b = (box_office - mean(box_office))/sd(box_office)
data2$std_b = std_b

d2 = data.frame(cbind(data2$Total_cases_Number, data2$std_b, data2$score.s, data2$Bscore.s))
names(d2) = c("Total_cases_Number","std_b","score_s","Bscore_s") 

d2$crime_cases = (d2$Total_cases_Number - mean(d2$Total_cases_Number))/sd(d2$Total_cases_Number)
```

#### Build Model

Build Model 2 with map.

```{r m2}
# Method 1
m2 <- map(
  alist(
    crime_cases ~ dnorm(mu, sigma),
    mu <- a +c1*std_b + c2*score_s + c3*Bscore_s,
    a ~ dnorm(0,10),
    c1 ~ dnorm(0,10),
    c2 ~ dnorm(0,10),
    c3 ~ dnorm(0,10),
    sigma ~ dunif(0,10)
  ),
  data <- d2,
  start<-list(a=mean(d2$crime_cases),c1=0,c2=0,c3=0, sigma=sd(d2$crime_cases)))
```

### Examining Model 2

#### Parameter Overview

From the pairs plot below, we can see that 

```{r m2.pairs}
pairs(m2)
```

We then examine the parameter estimates of Model 2.

```{r m2.precis}
precis(m2)
```

#### Parameter Effects

The effect of box office results and movie scores are shown below:

1. Box office results: std.b

```{r m2.box}
std_b.seq <- seq(from = -3, to = 3, length.out = 100)
mu <- link(m2, data = data.frame(std_b = std_b.seq, score_s = mean(d2$score_s), Bscore_s = mean(d2$Bscore_s)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ std_b, data = d2)
lines(std_b.seq, mu.mean)

shade(mu.PI, std_b.seq)
```

2. Movie scores: score.s

```{r m2.score}
score_s.seq <- seq(from = -1, to = 1, length.out = 100)
mu <- link(m2, data = data.frame(score_s = score_s.seq, std_b = mean(d2$std_b), Bscore_s = mean(d2$Bscore_s)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ score_s, data = d2)
lines(score_s.seq, mu.mean)

shade(mu.PI, score_s.seq)
```

3. Interaction between box office results and movie scores:

```{r m2.boxscore}
Bscore_s.seq <- seq(from = -6, to = 9, length.out = 100)
mu <- link(m2, data = data.frame(score_s = mean(d2$score_s), std_b = mean(d2$std_b), Bscore_s = Bscore_s.seq))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bscore_s, data = d2)
lines(Bscore_s.seq, mu.mean)

shade(mu.PI, Bscore_s.seq)
```

## Model 2 With Stan

### Building Model 2 With Stan

#### Build Model

Build Model 2 with map2stan.

```{r m2.stan}
# Method 2
m2.stan <- map2stan( m2, data<-d2, iter = 1e4, warmup = 1000) 
```

### Examining Model 2 With Stan

#### Parameter Overview

From the pairs plot below, we can see that 

```{r m2.stan.pairs}
pairs(m2.stan)
```

We then examine the parameter estimates of Model 2 with Stan.

```{r m2.stan.precis}
precis(m2.stan)
```

#### Parameter Effects

The effect of box office results and movie scores are shown below:

1. Box office results: std.b

```{r m2.stan.box}
std_b.seq <- seq(from = -3, to = 3, length.out = 100)
mu <- link(m2.stan, data = data.frame(std_b = std_b.seq, score_s = mean(d2$score_s), Bscore_s = mean(d2$Bscore_s)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ std_b, data = d2)
lines(std_b.seq, mu.mean)

shade(mu.PI, std_b.seq)
```

2. Movie scores: score.s

```{r m2.stan.score}
score_s.seq <- seq(from = -1, to = 1, length.out = 100)
mu <- link(m2.stan, data = data.frame(score_s = score_s.seq, std_b = mean(d2$std_b), Bscore_s = mean(d2$Bscore_s)))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ score_s, data = d2)
lines(score_s.seq, mu.mean)

shade(mu.PI, score_s.seq)
```

3. Interaction between box office results and movie scores:

```{r m2.stan.boxscore}
Bscore_s.seq <- seq(from = -6, to = 9, length.out = 100)
mu <- link(m2.stan, data = data.frame(score_s = mean(d2$score_s), std_b = mean(d2$std_b), Bscore_s = Bscore_s.seq))
mu.mean <- apply(mu, 2, mean)
mu.PI <- apply(mu, 2, PI, prob = 0.95)

plot(crime_cases ~ Bscore_s, data = d2)
lines(Bscore_s.seq, mu.mean)

shade(mu.PI, Bscore_s.seq)
```